Naming Anonymous JavaScript Functions

### 2011-04-12 papers/splash-wavefront2011/sigplanconf-template.tex
add examples table

\section{Building Up Intuition by Example}
We know that we face an ill-defined task: we are after all attempting to create short useful names for nameless functions. We have to create salient information from source code: we anticipate removing characters will be our biggest challenge.  To create an algorithm we decided to study the spectrum of examples from our 10 large collections of functions. We want to see what kinds of cases are important and what aspects of these cases help us identify functions.

@@

\subsection{Case 2: Entry in an Array Literal}
Contrary to the previous case the appearance of this case is very limited. It usually appears in initializations or when an array of functions are passed as an argument. Among all projects only two have instances of nameless functions defined in this way. For example array argument to \verb|Event._attach| in this example from YUI:
\begin{verbatim}
_attach: function (el, notifier, delegate) {
  if (Y.DOM.isWindow(el)) {
    return Event._attach([type, function (e) {
         notifier.fire(e);
    }, el]);
  }
}
\end{verbatim}
(The example is nested in more function definitions we do not show here). The developer will probably think of the array entry one item in a collection passed to \verb|Event._attach|. In general we shall want to name these kinds of functions by the destiny of the containing array.

\subsection{Case 3: Property Assignment With Property Identifier}
This case is the second most common case in the studied projects. Here, we can see why the Closure project is different from other projects in the first case. About 94\% of nameless functions in this project are defined in this way. It seems that the Closure developers follow an internal standard for function objects creation and usage.

@@

\subsection{Case 6:  Property Assignment With  Property Name Expressions}
Object member names can be expressions that get converted to strings at runtime: this is more general than case 5. 
 A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condition?"prop1":"prop2"}}, where the property that we assign the function to depends upon runtime values. Another kind of example of computed names comes from the Prototype project (refomatted to fit in the page):
\begin{verbatim}
  function define(D) {
    if (!element) element = getRootElement();
    property[D] = 'client' + D;
    viewport['get' + D] = function() { 
      return element[property[D]] 
    };
    return viewport['get' + D]();
  }
\end{verbatim}
The word \verb|get| is concatenated with the \verb|toString()| value of the argument \verb|D| at runtime to create the property name.  Unlike Case 5, the property name expression need not be a simple developer-invented identifier. In this example, \verb|viewport[getD]| could be a good name, but in general we will need to process the expression to balance length with information.

@@

\subsection{Case 8: Assignment to a Variable }
As the functions are immutable objects, it is very likely that a function object which is assigned to a variable, is used with the same variable name in the function scope
and its internal scopes. Although, there are cases that the variable name is temporary as the function is passed to another function or assigned to an object property, in most cases the variable name works will as the function name.

@@

\subsection{Case 10: Function Property is Accessed}
In this unusual case a property of the function is accessed directly from the function body. This case usually happens one of the predefined functions of function object (i.e., {\small\texttt{call, apply, bind}}) or when the predefined functions are augmented by adding to {\small\texttt{Function}} prototype.  Here is an example, from ExtJS, reformatted for display here:
\begin{verbatim}
setVisible : function(v, a, d, c, e){
    if(v){
        this.showAction();
    }
    if(a && v){
        var cb = function(){
            this.sync(true);
            if(c){
                c();
            }
        }.createDelegate(this);
   }
   // .....
}
\end{verbatim}
The inner function body is not used directly, but the result of \verb|createDelegate| is assigned to \verb|cb|. The most valuable information here is the variable name \verb|cb|, followed by the \verb|createDelegate| function name.  This example also illustrates that automatic naming could have an effect on developers coding style:  giving a longer name for \verb|cb| would give better names in development tools but currently developers have limited expectations that tools will show such information.

@@

\subsection{Examples}
\label{sec:examples}
To further explain our approach we now apply it to the JavaScript code presented in Figure~\ref{js-code}. We can recognize five function bodies in the code, none of them has a name.

@@

@@

To best of our knowledge, this paper is the first study in naming anonymous functions in JavaScript. H{\o}st and {\O}stvold \cite{Host} attempted to find and fix inappropriate function names in Java programs. Their approach employ rules extracted from a big corpus of Java projects to recognize buggy names. To fix a name a list of candidate names are constructed and ranked, the the name with highest rank is proposed for the replacement. This approach assumes that the function is already named and constructs the names based on the function internal structure. In contrast, our approach construct the function name by analysing the function context.

Caprile and Tonella \cite{Caprile}, analyse the structure of function identifiers in C programs. The identifiers are decomposed into fragments that are then classified into seven lexical categories. The structure of the function identifiers are futher described by a hand-crafted grammar.
%JavaScript, unlike many traditional object oriented languages such as Java and C\#, does not have classes, and does not encourage encapsulation or even structured programming. JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards}. As a direct consequence, the JavaScript code contains less explanatory data about the program elements and their relations. For example, the value of a variable can be a primitive value, an object with any structure or even a function. One call-site may invoke different function bodies with various number of arities that none of them can be understood from the code. Therefore, the lack of descriptive data in JavaScript code is the most fundamental issue in enhancing JavaScript tool support.

>>>>

\section{Building Up Intuition by Example}
\label{sec:intuition}
We know that we face an ill-defined task: we are after all attempting to create short useful names for nameless functions. We have to create salient information from source code: we anticipate removing characters will be our biggest challenge.  To create an algorithm we decided to study the spectrum of examples from our 10 large collections of functions. We want to see what kinds of cases are important and what aspects of these cases help us identify functions.

@@

\subsection{Case 2: Entry in an Array Literal}
\label{sec:arrayLiteral}
Contrary to the previous case the appearance of this case is very limited. It usually appears in initializations or when an array of functions are passed as an argument. Among all projects only two have instances of nameless functions defined in this way. For example array argument to \verb|Event._attach| in this example from YUI:
\begin{verbatim}
_attach: function (el, notifier, delegate) {
  if (Y.DOM.isWindow(el)) {
    return Event._attach([type, function (e) {
         notifier.fire(e);
    }, el]);
  }
}
\end{verbatim}
(The example is nested in more function definitions we do not show here). The developer will probably think of the array entry one item in a collection passed to \verb|Event._attach|. In general we shall want to name these kinds of functions by the destiny of the containing array.

\subsection{Case 3: Property Assignment With Property Identifier}
\label{sec:propid}
This case is the second most common case in the studied projects. Here, we can see why the Closure project is different from other projects in the first case. About 94\% of nameless functions in this project are defined in this way. It seems that the Closure developers follow an internal standard for function objects creation and usage.

@@

\subsection{Case 6:  Property Assignment With  Property Name Expressions}
\label{sec:propexpressions}
Object member names can be expressions that get converted to strings at runtime: this is more general than case 5. 
 A common case of expression in this case is a conditional expression, e.g., {\small\texttt{condition?"prop1":"prop2"}}, where the property that we assign the function to depends upon runtime values. Another kind of example of computed names comes from the Prototype project (refomatted to fit in the page):
\begin{verbatim}
  function define(D) {
    if (!element) element = getRootElement();
    property[D] = 'client' + D;
    viewport['get' + D] = function() { 
      return element[property[D]] 
    };
    return viewport['get' + D]();
  }
\end{verbatim}
The word \verb|get| is concatenated with the \verb|toString()| value of the argument \verb|D| at runtime to create the property name.  Unlike Case 5, the property name expression need not be a simple developer-invented identifier. In this example, \verb|viewport[getD]| could be a good name, but in general we will need to process the expression to balance length with information.

@@

\subsection{Case 8: Assignment to a Variable }
This case is widely used and we expect  developers would expect the function body to get the name of the variable.
As the functions are immutable objects, it is very likely that a function object which is assigned to a variable, is used with the same variable name in the function scope
and its internal scopes. There are cases in which a variable name is used temporarily, as the function is passed to another function or assigned to an object property. However, in most cases the variable name works well as the function name.

@@

\subsection{Case 10: Function Property is Accessed}
\label{sec:funcprop}
In this unusual case a property of the function is accessed directly from the function body. This case usually happens one of the predefined functions of function object (i.e., {\small\texttt{call, apply, bind}}) or when the predefined functions are augmented by adding to {\small\texttt{Function}} prototype.  Here is an example, from ExtJS, reformatted for display here:
\begin{verbatim}
setVisible : function(v, a, d, c, e){
    if(v){
        this.showAction();
    }
    if(a && v){
        var cb = function(){
            this.sync(true);
            if(c){
                c();
            }
        }.createDelegate(this);
   }
   // .....
}
\end{verbatim}
The inner function body is not used directly, but the result of \verb|createDelegate| is assigned to \verb|cb|. The most valuable information here is the variable name \verb|cb|, followed by the \verb|createDelegate| function name.  This example also illustrates that automatic naming could have an effect on developers coding style:  giving a longer name for \verb|cb| would give better names in development tools but currently developers have limited expectations that tools will show such information.

@@

\subsection{Examples}
\label{sec:examples}

\begin{table*}[tb]
\centering
\begin{tabular}{|l|l|}
\hline
Example Code & Static Function-Object Consumption Name \\
\hline
Sec.~\ref{sec:arrayLiteral} & YUI.add[event-focus]()/\_attach/Event.\_attach() \\
\hline
Sec.~\ref{sec:propid} & eventPool\_createObject \\
\hline
Fig.~\ref{fig:jQueryEach} outer & jQuery.each(ajaxStart) \\
\hline
Fig.~\ref{fig:jQueryEach} inner & jQuery.fn[o] \\
\hline
Sec.~\ref{sec:propexpressions}  & define/viewport[get+D] \\
\hline
Fig.~\ref{fig:classnamemanager} outer & YUI.add[classnamemanager]()/Y.ClassNameManage\verb|<| \\
\hline
Fig.~\ref{fig:classnamemanager} inner & YUI.add[classnamemanager]()/Y.ClassNameManager/getClassName \\
\hline
Sec.~\ref{sec:funcprop} inner & ?????????????\\
\hline
Fig.~\ref{fig:registerWin} inner & registerWin\verb|<| \\
\end{tabular}
\label{table:examples}
\caption{Results from applying the approach in Sec.~\ref{sec:foc} to the examples in the paper at the point given in the first column.
Full names are listed, even in cases where our example code omitted the enclosing function scope.}
\end{table*}

To further explain our approach we now apply it to the JavaScript code presented in Figure~\ref{js-code}. We can recognize five function bodies in the code, none of them has a name.

@@

Finally, Table~\ref{table:examples} gives the names of functions from examples discussed in \ref{sec:intuition}.

@@

To best of our knowledge, this paper is the first study in naming anonymous functions in JavaScript. H{\o}st and {\O}stvold \cite{Host} attempted to find and fix inappropriate function names in Java programs. Their approach employs rules extracted from a big corpus of Java projects to recognize buggy names. To fix a name a list of candidate names are constructed and ranked, the the name with highest rank is proposed for the replacement. This approach assumes that the function is already named and constructs the names based on the function internal structure. In contrast, our approach construct the function name by analyzing the function context.

Caprile and Tonella \cite{Caprile}, analyse the structure of function identifiers in C programs. The identifiers are decomposed into fragments that are then classified into seven lexical categories. The structure of the function identifiers are further described by a hand-crafted grammar.
%JavaScript, unlike many traditional object oriented languages such as Java and C\#, does not have classes, and does not encourage encapsulation or even structured programming. JavaScript is a weakly typed language with no type declarations and only run-time checking of calls and field accesses \cite{Richards}. As a direct consequence, the JavaScript code contains less explanatory data about the program elements and their relations. For example, the value of a variable can be a primitive value, an object with any structure or even a function. One call-site may invoke different function bodies with various number of arities that none of them can be understood from the code. Therefore, the lack of descriptive data in JavaScript code is the most fundamental issue in enhancing JavaScript tool support.
